---
author: "Cecilia Leon"
output:
  html_document:
    toc: yes
title: "Query 1: Elections"
date: "`r format(Sys.time(), '%d %B, %Y')`"
params:
  argstart: !r Sys.Date()
  argend: !r Sys.Date() + 1
---

This file shows a sample of the code that was employed to collect data from Twitter


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rtweet)
library(mongolite)
library(jsonlite)
library(ggplot2)
library(kableExtra)
library(lubridate)
```

To run the first query (Elections) we are going to use the credentials that we have in the following twitter's account,the access tokens can be found [here](https://developer.twitter.com/en/apps/16341710).

| Field | Value |
|------|-----|
| Username|  |
| Password |  |
| App |  |

```{r tokens_rtweet , echo = FALSE}
token <- create_token(
  app = "Test full archive API",
  consumer_key = 
  consumer_secret = 
  access_token = 
  access_secret = )
```

The number of documents before running the query is:

```{r connect_elections}
m_elections <- mongo(collection = "Elections", 
                     url = "")

m_elections$count()
```


```{r config_search, results="hide"}
#config
from <- params$argstart 
to <- params$argend
limit <- 100000

#summary
sum_find <- m_elections$find(query = '{}',fields = '{"timestamp_CAD":1,"id":1}')
day <- sum_find$timestamp_CAD
complete_days <- table(day)[-c(1)]
```

We run the query *Elections* on **`r from`** with a limit of `r show_num(limit, 0)` requests per day. This appears to be `r ifelse( limit > max(complete_days) ,"APPROPIATE", "WRONG")` according to the historical behaviour that daily mentions have shown.

```{r histiric_graph, echo = FALSE}
aux_df <- data.frame(complete_days)

if(dim(aux_df)[1]>1){
  aux_df$day <- as.Date(as.character(aux_df$day))

  ggplot(aux_df, aes(day,Freq,group = 1)) +
  geom_line(color='steelblue') +
  geom_point(size = 1, color='steelblue') +
  xlab("") + 
  ylab("Number of tweets") +
  ggtitle("Daily tweets count about 43rd Canadian Elections")
}
```

**Summary**

```{r, echo = FALSE}
s_table <- rbind(max(complete_days),
                 min(complete_days),
                 mean(complete_days),
                 sd(complete_days)
                 )

rownames(s_table) <- c("  Maximum  ","  Minumim  ","  Mean  ","  Sd  ")

kable(s_table, 
      digits= 0,
      align = "c",
      row.names = TRUE)  %>%
  kable_styling(full_width = TRUE)
```


```{r insertion_twitteR, include = FALSE, eval = FALSE}
last_sinceID <- ifelse(length(sum_find)==0,0,max(sum_find$id))

tweets_query1 <- searchTwitter('"canadian elections"+OR+"2019 canada federal election"+OR+"canadian general election"+OR+#CanadaElection2019+OR+#elxn43+OR+#canadaelection+OR+#electioncanada2019+OR+#Elections2019+OR+(("canadian elections"+OR+"2019 canada federal election"+OR+"canadian general election"+OR+#CanadaElection2019+OR+#canadaelection)+#cdnpoli)', 
                     resultType="recent",
                     geocode ='54.751594238071675,-126.00017214111986,700mi',
                     n = limit,
                     since = from,
                     until = to,
                     sinceID = last_sinceID)
```

So, we perform the following query:


```{r tAPI_rtweet}
tweets_query1 <- search_tweets(
  q = '(canadian (election OR elections)) OR (canada (election OR elections)) OR #CanadaElection2019 OR #elxn43 OR #canadaelection OR #electioncanada2019 OR #Elections2019 OR ( (canadian (election OR elections)) OR (canada (election OR elections)) OR #CanadaElection2019 OR #elxn43 OR #canadaelection OR #electioncanada2019 OR #Elections2019 #cdnpoli)',
  type = "recent",
  n = limit, 
  include_rts = TRUE,
  geocode = '54.751594238071675,-126.00017214111986,700mi',
  since = from,
  until = to,
  retryonratelimit = TRUE,
  lang = "en"
  )
```

The number of found tweets is **`r dim(tweets_query1)[1]`**. These documents are going to be inserted in the collection *Elections*.

```{r insertion_rtweet, echo = FALSE}

if(length(tweets_query1)==0){
  print("No more tweets to record")    
}else{
  tweets_query1$timestamp <- substr(tweets_query1$created_at,1,10)
  tweets_query1$created_at_CAD <- tweets_query1$created_at - 25200
  tweets_query1$timestamp_CAD <- substr(tweets_query1$created_at_CAD,1,10)
  tweets_query1$week <- paste0(substr(tweets_query1$timestamp_CAD,1,4),"-",isoweek(tweets_query1$timestamp_CAD))
  tweets_query1$tg_elections <- 1
}

modifiedCount <- matchedCount <- upsertedCount <- c()

for(i in 1:dim(tweets_query1)[1]){
  aux_doc <- toJSON(tweets_query1[i,])
  aux_update <- m_elections$update(paste0('{"status_id":"',tweets_query1$status_id[i],'"}'),
                     paste0('{"$set":',substr(aux_doc,2,nchar(aux_doc)-1),'}'),
                     upsert = TRUE)
  modifiedCount[i] <- aux_update$modifiedCount
  matchedCount[i] <- aux_update$matchedCount
  upsertedCount[i] <- aux_update$upsertedCount
}
```

```{r update_summary}
print(paste0("modifiedCount: ",sum(modifiedCount)))
print(paste0("matchedCount: ",sum(matchedCount)))
print(paste0("upsertedCount: ",sum(upsertedCount)))
```

After the insertion of **`r show_num(sum(upsertedCount))`** documents that correspond to the generated tweets at **`r from`**, the collection has a new number of records, which is:

```{r new_counts}
m_elections$count()
```

Finally, we disconnect from the database.

```{r disconnect}
m_elections$disconnect()
```



